The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-03-30 VegOzone.tex
Removed Prestebakke.

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs}
  \caption{Multi-annual mean of daily mean ozone at observation sites in Fennoscandia. For comparison also data from Prestebakke (southern Norway) is shown. The large spread in case of Svanvik and Janiskoski is due to the lower statistics. All northern Fennoscandic climatologies peak in spring, with peak values in April. In southern Norway, peak values appear only in May. The annual average ozone concentration \chem{\left<[O_3]\right>} at Svanvik is $6.6\,\unit{ppb}$ lower than at the sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN).}
  \label{fig:ozone_climatology_fenoscandic_obs}
\end{figure}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_climatologies}
  \caption{Comparison of climatologies (northern Fennoscandia -- black and southern Fennoscandia -- grey) derived from observational data (EBAS, see Fig.~\ref{fig:ozone_climatology_fenoscandic_obs}) with various ozone reanalysis products (ECMWF: MACC/CAMS reanalysis, Copernicus: Regional model reanalysis ensemble mean). As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis is in general too low and displays a erroneous seasonal cycle. The CAMS reanalysis matches quite well in southern Fennoscandia but does not reproduce the seasonality in northern Fennoscandia. The ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in both northern and southern Fennoscandia, though the ozone concentrations in the north are slightly to low.}
  \label{fig:ozone_climatologies}
\end{figure*}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_residuals}
  \caption{Probability density functions of ozone concentration residuals. 2018 with respect to respective climatology for different sites in Fennoscandia. (a) Esrange; (b) Pallas; (c) Prestebakke.}
  \label{fig:ozone_climatology_fenoscandic_obs_residuals}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_test}
  \caption{Student's t-test assuming same sample uncertainty in both, climatology and 2018 observations for different sites in Fennoscandia. \chem{\Delta[O_3]} in Fig.~\ref{fig:ozone_climatology_fenoscandic_obs_residuals} are significantly different from zero-hypothesis on the $1\,\sigma$ level. (a) Esrange; (b) Pallas; (c) Prestebakke.}
  \label{fig:ozone_climatology_fenoscandic_obs_test}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{test_fennoscandia}
  \caption{Maximum daily sun shine duration based on geometrical calculations at different sites in Fennoscandia. Midnight sun conditions at Jergul/Karasjok and Svanvik prevail from the end of May until the end of July, while at Esrange and Pallas they only prevail from the beginning of June until mid of July. For comparison with southern Fennoscandia, Prestebakke is shown.}
  \label{fig:sunlight_fennoscandia}
\end{figure}

>>>>

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs}
  \caption{Multi-annual mean of daily mean ozone at observation sites in Fennoscandia. The large spread in case of Svanvik and Janiskoski is due to the lower statistics. All northern Fennoscandic climatologies peak in spring, with peak values in April. In southern Norway, peak values appear only in May. The annual average ozone concentration \chem{\left<[O_3]\right>} at Svanvik is $6.6\,\unit{ppb}$ lower than at the sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN).}
  \label{fig:ozone_climatology_fenoscandic_obs}
\end{figure}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_climatologies}
  \caption{Comparison of climatologies (northern Fennoscandia -- black and southern Fennoscandia -- grey) derived from observational data (EBAS, see Fig.~\ref{fig:ozone_climatology_fenoscandic_obs}) with various ozone reanalysis products: (a) ECMWF: MACC reanalysis; (b) ECMWF: CAMS reanalysis; (c) Copernicus: Regional model reanalysis ensemble mean. As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis is in general too low and displays a erroneous seasonal cycle. The CAMS reanalysis matches quite well in southern Fennoscandia but does not reproduce the seasonality in northern Fennoscandia. The ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in both northern and southern Fennoscandia, though the ozone concentrations in the north are slightly to low.}
  \label{fig:ozone_climatologies}
\end{figure*}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_residuals}
  \caption{Probability density functions of ozone concentration residuals. 2018 with respect to respective climatology for different sites in Fennoscandia. (a) Esrange; (b) Pallas.}
  \label{fig:ozone_climatology_fenoscandic_obs_residuals}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_test}
  \caption{Student's t-test assuming same sample uncertainty in both, climatology and 2018 observations for different sites in Fennoscandia. \chem{\Delta[O_3]} in Fig.~\ref{fig:ozone_climatology_fenoscandic_obs_residuals} are significantly different from zero-hypothesis on the $1\,\sigma$ level. (a) Esrange; (b) Pallas.}
  \label{fig:ozone_climatology_fenoscandic_obs_test}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{test_fennoscandia}
  \caption{Maximum daily sun shine duration based on geometrical calculations at different sites in Fennoscandia. Midnight sun conditions at Jergul/Karasjok and Svanvik prevail from the end of May until the end of July, while at Esrange and Pallas they only prevail from the beginning of June until mid of July.}
  \label{fig:sunlight_fennoscandia}
\end{figure}
